The finite base property for some subreducts of representable relation algebras

### 2020-07-12 problem-19.17/Text.tex
formulate the claim for representability of the ultraproduct

@@

@@

\begin{proof}
  The valuation $\vartheta$ defined as:
  \begin{enumerate}
    \item $\vartheta(x) = {\bf w}$
    \item $\vartheta(x_i^{'}) = {\bf g}_i$
    \item $\vartheta(x_i^{''}) = {\bf y}_i$
    \item $\vartheta(y) = {\bf i}$
    \item $\vartheta(y_i^{'}) = {\bf r}_i$
    \item $\vartheta(y_i^{''}) = {\bf b}_i$
  \end{enumerate}
  falsifies $q_n$ in $\mathfrak{A}_n$
\end{proof}

@@

\begin{lemma}
  Let $\mathcal{A}$ be an atomic relation algebra. Then $\exists$ has a winning strategy in $\mathcal{G}_n({\mathcal{A}})$ for each $n < \omega$ iff $\mathcal{A}$ is elementary equivalent to some completely representable relation algebra. If $\exists$ has a winning strategy, then $\mathcal{A}$ is representable since ${\bf RRA}$ is elementary.
\end{lemma}

@@

\begin{lemma}
  TODO: one needs to realise when $\exists$ has a winning strategy
\end{lemma}

>>>>

\theoremstyle{claim}
\newtheorem{claim}{Claim}

@@

\subsection{The rainbow construction}

@@

\begin{proof}
  The valuation $\vartheta$ defined as:
  \begin{enumerate}
    \item $\vartheta(x) = {\bf w}$
    \item $\vartheta(x_i^{'}) = {\bf g}_i$
    \item $\vartheta(x_i^{''}) = {\bf y}_i$
    \item $\vartheta(y) = {\bf i}$
    \item $\vartheta(y_i^{'}) = {\bf r}_i$
    \item $\vartheta(y_i^{''}) = {\bf b}_i$
  \end{enumerate}
  falsifies $q_n$ in $\mathfrak{A}_n$.

  TODO: visualise the reason for non-representability.
\end{proof}

\subsection{Networks and games}

@@

\begin{lemma} \label{win}
  Let $\mathcal{A}$ be an atomic relation algebra. Then $\exists$ has a winning strategy in $\mathcal{G}_n({\mathcal{A}})$ for each $n < \omega$ iff $\mathcal{A}$ is elementary equivalent to some completely representable relation algebra. If $\exists$ has a winning strategy, then $\mathcal{A}$ is representable since ${\bf RRA}$ is elementary.
\end{lemma}

\subsection{The ultraproduct}

@@

According to the following claim, $\exists$ has a winning strategy on cofinitely many algebras that allows her to win a game on the ultraproduct. Thus, according to Lemma~\ref{win}, the ultraproduct belongs to ${\bf RRA}$.

\begin{claim}
  Let $l < \omega$. $\exists$ has a winning strategy for $G_l(\mathfrak{A}_n)$ for cofinitely many algebras beloging to the sequence $\{ \mathfrak{A}_n \}_{n < \omega}$.
\end{claim}

\begin{proof}
  Let $n \geq l$. We show that $\exists$ has a winning strategy for $G_l(\mathfrak{A}_n)$.
\end{proof}
